---
title: "R Assessment"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
options(warn = -1) 
knitr::opts_chunk$set(echo = TRUE)
```

In this Assessment we will analyze a dataset of ad impressions. Each entry in this dataset is an impression id, information about the customer and 

## Setting Up 

1. Install RStudio on your computer. Create a directory named ``Assessment`` somewhere on your computer and add an empty file named ``answers.R`` in it. Switch to that directory in RStudio and set the directory as your current working directory. Upload an image. 

2. Clear all variables in the workspace. It's best to do this before any project.
```{r}
rm(list=ls())
```


3. In this exercise we will need the ``dplyr`` and ``ggplot2`` libraries. Install these packages if you don't have it, otherwise load it. 

```{r}
library('dplyr')
library('ggplot2')
```
4. Load the file ``data1.csv`` into the data frame ``ads``. 

```{r}
ads <- read.csv('data1.csv')
```

## Basic Data Analysis

4. What are the column names of this data frame?
```{r}
colnames(ads)
```

5. How may rows does the data frame have?
```{r}
nrow(ads)
```


6. Give an initial summary of the data frame
```{r}
summary(ads)
```

7. Count up the total number of conversions over all ads.
```{r}
sum(ads$conversion)
```

8. Filter our all impressions from the ``display`` channel that cost over $1. Save the result in the data frame ``expensive.ads``

```{r}
expensive.ads<- ads[(ads$cost > 1)& (ads$channel=='display'),]
```


9. For the ads in the previous question, what was the total spent?
```{r}
sum(expensive.ads$cost)
```

## Datatable Manipulation


9. Add a column which for each ad represents the profit. Compute the total profit.

```{r}
ads$profit <- ads$revenue - ads$cost
sum(ads$profit)
```

10. Create a new data frame that for each channel shows the total impressions, total conversions, and total cost.

```{r}
channel.per <- ads %>% group_by(channel) %>% summarise(total.impressions=n(), total.conversions=sum(conversion), total.cost=sum(cost))
print(channel.per)
```

11. Now import ``data2.csv`` into a data frame called ``customers`` and merge ``ads`` and ``customers``  on ``id`` calling the final data frame ``merged``.
```{r}
customers <- read.csv('data2.csv')
merged <- merge(ads,customers,by="id")
```
## Analysis

12. Construct a regression between the age of the customers and spend of a customer. 
```{r}
reg1 <- lm(revenue~age, data=merged)
print(reg1)
```
13. What is the $R^2$ of this regression?
```{r}
summary(reg1)
```

14. Using the regression predict the spend of a customer who is 38.
```{r}
predict(reg1, newdata = data.frame(age = c(38)))
```


15. Using GLM, construct a regression between the Ad type and the conversions.
```{r}
reg2 <- glm(conversion~type, data=merged, family='binomial')
print(reg2)
```

16. What coefficients appear in the previous regression? 
```{r}
reg2 <- glm(conversion~type, data=merged, family='binomial')
summary(reg2)
```

17. Perform a t-test between the conversions of the ad with type A and the ad with type B. What's the p-value?
```{r}
adA <- merged[merged$type=='A',]
adB <- merged[merged$type=='B',]
t.test(adA$conversion,adB$conversion)
```


## Plotting

13. Plot the ages of customers against their revenue along with the regression line you learned above.
```{r}
ggplot(merged, aes(age, revenue)) + geom_point()
```
14. Plot a histogram on the set of costs.

```{r}
ggplot(merged, aes(cost)) + geom_histogram(binwidth=.1)
```
<!--```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.-->
