---
title: "R Assessment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this Assessment we will analyze a dataset of ad impressions. Each entry in this dataset is an impression id, information about the customer and 

## Setting Up 

1. Install RStudio on your computer. Create a directory named ``Assessment`` somewhere on your computer and add an empty file named ``answers.R`` in it. Switch to that directory in RStudio and set the directory as your current working directory. Upload an image. 

2. Clear all variables in the workspace. It's best to do this before any project.
```{r}
rm(list=ls())
```


3. In this exercise we will need the ``dplyr`` library. Install this package if you don't have it, otherwise load it. 

```{r}
library('dplyr')
```
4. Load the file ``data1.csv`` into the dataframe ``ads``. 

```{r}
ads <- read.csv('data1.csv')
```

## Basic Data Analysis

4. What are the column names of this dataset?
```{r}
colnames(ads)
```

5. How may rows does the dataset have?
```{r}
nrow(ads)
```


6. Give an initial summary of the dataset.
```{r}
summary(ads)
```

7. Count up the total number of conversions over all ads.
```{r}
sum(ads$conversion)
```

8. Filter our all impressions from the ``display`` channel that cost over $1. Save the result in the datatable ``expensive.ads``

```{r}
expensive.ads<- ads[(ads$cost > 1)& (ads$channel=='display'),]
```


9. For the ads in the previous question, what was the total spent?
```{r}
sum(expensive.ads$cost)
```

## Datatable Manipulation

9. Some impression id's are duplicated. Remove the duplicates.

10. Add a column which for each ad represents the profit. Compute the total profit.

```{r}
ads$profit <- ads$revenue - ads$cost
sum(ads$profit)
```

11. Create a new dataframe that for each channel shows the total impressions, total conversions, and total cost.

```{r}
channel.per <- ads %>% group_by(channel) %>% summarise(total.impressions=n(), total.conversions=sum(conversion), total.cost=sum(cost))
print(channel.per)
```

12. Something about merging?

## Modeling

10. Something about lm and glm


## Plotting

<!--```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.-->
